Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-12-14 presentations/illustrations/linear-prevention.tex
added missing capability and removed slides that had been duplicated

\begin{frame}
  \frametitle{Linear caps prevents attack 3}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
  \stdstackstart

  \begin{onlyenv}<+->
    \actsf{(0,2.5)}{(6,5.5)}{caller stack frame}
    \draw[fill=white] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
  \end{onlyenv}

  % Note: the return pointer actually spans all of the available stack, but for space reasons, we only draw part of it here.
  \begin{onlyenv}<+->
    \begin{scope}
      \clip (6.1,2.5) rectangle (8.1,5.5);
      \capbrace[ret1]{(6.1,2.5)}{(6.1,6.5)}
    \end{scope}
    \draw node[fill=gray!50,right=0cm of ret1] { \phantom{ret-ptr} };
    \draw node[right=0cm of ret1] { ret-ptr };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=white] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \actadv{(0,5.5)}{(6,8.5)}{callee stack frame}
  \end{onlyenv}

  \begin{onlyenv}<+-.(2)>
    \draw (13,4.75) edge[red,bend right,thick,->] (ret1);
  \end{onlyenv}

  \begin{onlyenv}<+>
    \draw[teal,very thick] (9,4.9) -- (12.5,5.9);
    \draw[teal,very thick] (9,5.9) -- (12.5,4.9);
    \draw node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white] () at (14,10) {Return pointer is local!};  
  \end{onlyenv}

  \begin{onlyenv}<+->
    \draw[fill=white] (0,13) rectangle (6,13.5) node[pos=.5,color=red] {\footnotesize copy of sp};
  \end{onlyenv}
  \draw<.> (6,13.25) edge[red,thick,->,in=45] (ret1);

  \begin{onlyenv}<+->
    \begin{scope}
      \clip (6.1,5.5) rectangle (8.1,8.5);
      \capbrace[ret2]{(6.1,5.5)}{(6.1,9.5)}
    \end{scope}
    \draw node[fill=gray!50,right=0cm of ret2] { \phantom{ret-ptr (1)} };
    \draw node[right=0cm of ret2] { ret-ptr (1) };
  \end{onlyenv}
  \draw<.-.(1)> (6,13.25) edge[red,thick,->,in=45] (ret1);

  \begin{onlyenv}<+->
    \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
    \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
    \actsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \draw[fill=white] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};

  \end{onlyenv}

  \begin{onlyenv}<+->
    \foreach \x in {11.5,12,...,14}
    {
      \draw[fill=white] (0,\x) rectangle (6,\x+.5) node[pos=.5,color=teal] {\footnotesize 0};
    };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \begin{scope}
      \clip (6.1,8.5) rectangle (8.1,11.5);
      \capbrace[ret3]{(6.1,8.5)}{(6.1,12.5)}
    \end{scope}
    \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr (2)} };
    \draw node[right=0cm of ret3] { ret-ptr (2) };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \inactsf{(0,2.5)}{(6,5.5)}{caller stack frame}
    \inactadv{(0,5.5)}{(6,8.5)}{callee stack frame}
    \inactsf{(0,8.5)}{(6,11.5)}{callee stack frame (1)}
    \actadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \draw[fill=gray!30] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};
    \draw[fill=white] (13,10) rectangle (18,12) node[pos=.5] {\footnotesize callee code (2)};
  \end{onlyenv}

  \begin{onlyenv}<+->
    \draw node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,4) {ret-ptr capability gone,\\can only access ret-ptr (2)!};  
  \end{onlyenv}
\end{tikzpicture}

@@

  \begin{onlyenv}<.-.(2)>
    \capbrace[sp]{(6.1,4.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

>>>>

@@

  \begin{onlyenv}<.-.(3)>
    \capbrace[sp]{(6.1,4.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}
